%! Author = Sten
%! Date = 29-09-2020

% Preamble
\documentclass[11pt]{article}

\usepackage[a4paper,margin=2.5cm]{geometry}

% Packages
\usepackage[fleqn]{amsmath}

\input{macros.tex}

\theoremstyle{definition}
\newtheorem{fact}{Fact}
\newtheorem{conjecture}{Conjecture}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}

\title{Generalizing the ring network proof}
\author{David Dekker \and Sten Wessel}
\date{\today}

% Document
\begin{document}
    \maketitle
    \hrule
    \medskip

    \section{Introduction}
    The paper by Grandoni et al.~\cite{grandoni2008short} gives a short proof that the VPN conjecture is true for the cases where the considered network is a ring.
    In the following, we will discuss whether it is possible to extend the proof to the generalized VPN conjecture, for the cases where the network is a ring and the demand tree is a \emph{two-union star}: the tree formed by connecting the centers of two star graphs.

    Some background of what steps we are taking is identical to what is described in \cite{grandoni2008short} and we will omit these details.
    We focus on showing the differences that are necessary in the proof to adapt to the generalized VPN problem setting.
    We use the same notation as used in the aforementioned paper, except where the generalized VPN problem differs from the VPN problem.

    \section{Generalized VPN setting}
    We consider an undirected graph $G = (V_G, E_G)$ with non-negative edge costs $c\colon E_G \to \reals_+$.
    A subset of the vertices are terminals $W \subseteq V_G$
    Traffic demands between terminals are be described by symmetric matrices $D = (d_ij)_{i,j \in W}$, where the non-negative entries $d_{ij} = d_{ji}$ describe the (undirected) traffic between two terminals $i,j \in W$.
    We assume the diagonal to be zero, i.e.\ $d_{ii} = 0$ for all $i \in W$.
    We define a universe of traffic demand matrices $\mathcal U_T$ that is described by an edge-capacitated tree $T = (V_T, E_T)$ with leaf set equal to the terminals $W$ and edge capacities $b\colon E_T \to \reals_+$.
    A traffic matrix belongs to $\mathcal U_T$ when it can be routed on $T$.

    A solution to the \emph{generalized VPN problem} defined by $(G, c, W, T, b)$ consists of a \emph{routing template} $\set{P_{ij}}_{i,j \in \binom{W}{2}}$ ($i$-$j$-paths in $G$ for each unordered pair of terminals), and `bought' edge capacities $u(e) \ge 0$ for all $e \in E_G$.
    A solution is \emph{feasible} all traffic demand matrices in $\mathcal U_T$ can be routed on $G$ according to the routing template, and without exceeding the edge capacities $u$.
    A solution is \emph{optimal} if it is feasible and minimizes $\sum_{e \in E_G} c(e) u(e)$.

    Note that the generalized VPN problem is equivalent to an original VPN problem instance when $T$ is a star.

    % TODO: define tree solution

    \subsection{Two-union star demand trees}
    For the remainder, we restrict ourselves to instances where $T$ is a \emph{two-union star}, that is, a tree formed by connecting the centers $r_1,\ r_2$ of two star graphs.
    We will call this edge $r = \set{r_1, r_2}$ and refer to it as the \emph{bridge} of $T$.

    \section{Preliminaries}
    A number of assumptions are made in \cite{grandoni2008short}, the most important being that we can assume the capacities $b \equiv 1$.
    We suspect this does not quite generalize to our case, but we can state the following:

    \begin{fact}
        We may assume $b(f) = 1$ when $f \neq r$.
    \end{fact}
    Using the same motivation as in \cite{grandoni2008short}, if the capacity $b(iu)$ for the terminal $i \in W$ is not unit, construct a new instance with new terminals $i_1, \dots, i_{b(iu)}$, connected to the site of $i$ in $G$, with edge cost $0$.
    Set the capacities of the incident edges in $T$ to unit.
    Note that this instance is equivalent, but may change the topology of the graph.

    An alternative construction is argued in \cite{grandoni2008short} to keep the topology a ring and we refer to this paper for the motivation.

    \begin{fact}
        We can assume $b$ to be integral.
    \end{fact}
    This is motivated by scaling by a sufficiently large factor (excluding weird irrational cases, but that is probably fine).

    % TODO: not sure if this is useful
%    \paragraph{Bound on bridge capacity}
%    Let $\set{r_1, r_2}$ be the bridge.
%    Let $W_1, W_2 \subseteq W$ denote the terminals connected to $r_1$ and $r_2$ in $T$, respectively.
%    Using that all capacities are unit (except for the bridge), we know that the maximum edge capacity is $\min\set{ |W_1|, |W_2| }$.
%    We motivate this as follows: the maximum amount of traffic that can cross the bridge is $\min\set{ |W_1|, |W_2| }$, hence no additional traffic matrices can be routed on a tree with larger bridge capacity.
%    Hence, trees with larger bridge capacity describe the same universe as using a tree with the argued maximum edge capacity.

    \section{Pyramidal Routing problem}
    To goal is to show that there exists an optimal solution to the generalized VPN problem that is a tree solution (or, equivalently, there exists a tree solution to the generalized VPN problem that is optimal).
    Consider an optimal tree solution $(\set{P_{ij}}, u)$ to a generalized VPN instance $(G, c, W, T, b)$, with $|W| = k$ and $T$ a two-union star with the unit capacity assumption as above.
    Let $\mathcal P_i$ be as in \cite{grandoni2008short} for a fixed $i \in W$.
    We define
    \[
        \xi(e, \mathcal P_i) \coloneqq \min\set{\alpha(e, \mathcal P_i),\ \beta(e, \mathcal P_i)} + \min\set{n(e, \mathcal P_i) - \alpha(e, \mathcal P_i),\ k - n(e, \mathcal P_i) - \beta(e, \mathcal P_i)}
    \]
    where
    \begin{gather*}
        n(e, \mathcal P_i) \coloneqq |\set{j \in W \setminus \set{i} : e \in P_{ij}}|,\\
        \alpha(e, \mathcal P_i) \coloneqq |\set{j \in W \setminus \set{i} : e \in P_{ij},\ r \in \pi_T(i, j)}|,\\
        \beta(e, \mathcal P_i) \coloneqq |\set{j \in W \setminus \set{i} : e \not\in P_{ij},\ r \not\in \pi_T(i, j)}|,
    \end{gather*}
    that is, $\alpha(e, \mathcal P_i)$ is the number of paths in $\mathcal P_i$ containing $e$, \emph{while simultaneously the path in the demand tree between $i$ and $j$ crosses the bridge}.
    In our setting, we have a different expression for the \emph{required} capacity of edge $e$:
    \[
        u(e) = \xi(e, \mathcal P_i) + \min\Big\{b(r),\ n(e, \mathcal P_i) - \xi(e, \mathcal P_i),\ k - n(e, \mathcal P_i) -  \xi(e, \mathcal P_i)\Big\}.
    \]
    We can now formulate the generalized Pyramidal Routing (\emph{genPR}) problem with instance $(G, c, W, T, b, i)$ as to minimize $\sum_{e \in E_G} c(e) y(e, \mathcal P_i)$ over all $\mathcal P_i$ (for an arbitrary fixed $i \in W$), where we define
    \[
        y(e, \mathcal P_i) = \xi(e, \mathcal P_i) + \min\Big\{b(r),\ n(e, \mathcal P_i) - \xi(e, \mathcal P_i),\ k - n(e, \mathcal P_i) -  \xi(e, \mathcal P_i)\Big\}.
    \]

    We now formulate our version of Conjecture~2 (as in \cite{grandoni2008short}).
    \renewcommand\theconjecture{2}
    \begin{conjecture}[The \emph{genPR} conjecture]
        For each \emph{genPR} instance $(G, C, W, i, T, b)$ there exists an optimal solution which is a tree solution.
    \end{conjecture}

    We now show our version of Theorem~1 (having the same formulation as in \cite{grandoni2008short}), using the equivalent of Lemma~3, Claim~1, and Claim~2.

    \renewcommand\thelemma{3}
    \begin{lemma}
        Consider an generalized VPN instance $(G, c, W, T, b)$ with $T$ a two-union star with bridge $r$, $b(f) = 1$ for $f \neq r$, and some feasible solution $(\set{P_{ij}}, u)$.
        There exists a terminal $i \in W$ such that $\sum_{e \in E_G} c(e) u(e) \ge \sum_{e \in E_G} c(e) y(e, \mathcal P_i)$, where $\mathcal P_i = \set{P_{ij} : j \in W \setminus \set{i}}$.
    \end{lemma}
    \begin{proof}
        Fix an edge $e \in E_G$.
        We define the same traffic matrix $D^e = (d^e_{ij})_{i,j \in W}$ as in \cite{grandoni2008short},
        \[
            d^e_{ij} = \begin{cases}
                           \frac 1 k \left( \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} + \frac{y(e, \mathcal P_j)}{n(e, \mathcal P_j)} \right) & \text{if $e \in P_{ij}$,} \\
                           0 & \text{otherwise.}
            \end{cases}
        \]

        Now, the proof of Claim~1 is slightly different, as our universe is described by a different set of inequalities.

        \renewcommand\theclaim{1}
        \begin{claim}
            $D^e \in \mathcal U_T$, that is
            \[
                \sum_{\substack{ij \in \binom{W}{2}:\\f \in \pi_T(i,j)}} d^e_{ij} \le b(f)
            \]
            for all $f \in E_T$.
        \end{claim}
        \begin{proof}
            We consider two cases:
            \begin{itemize}
                \item $f \neq r$, hence we can write $f = f_i$, where $f_i \in E_T$ is the edge incident some terminal $i \in W$.
                Now note that we can write
                \[
                    \sum_{\substack{\ell j \in \binom{W}{2}:\\f_i \in \pi_T(\ell,j)}} d^e_{\ell j} = \sum_{j \in W \setminus \set{i}} d^e_{ij}
                \]
                as $f_i$ is exactly in all paths from/to $i$ in the tree, as it is the edge incident to $i$.
                The rest of this case follows the same steps as the proof in \cite{grandoni2008short}:
                \[
                    \begin{split}
                        \sum_{\substack{\ell j \in \binom{W}{2}:\\f_i \in \pi_T(\ell,j)}} d^e_{\ell j} &= \sum_{j \in W \setminus \set{i}} d^e_{ij} \\
                        &= \frac 1 k \sum_{\substack{j \in W \setminus \set{i}:\\ e \in P_{ij}}} \left( \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} + \frac{y(e, \mathcal P_j)}{n(e, \mathcal P_j)} \right) \\
                        &\le \frac 1 k \sum_{\substack{j \in W \setminus \set{i}:\\ e \in P_{ij}}} \left( \frac{k - n(e, \mathcal P_i)}{n(e, \mathcal P_i)} + \frac{n(e, \mathcal P_j)}{n(e, \mathcal P_j)} \right) \\
                        &= \frac{1}{n(e, \mathcal P_i)} \sum_{\substack{j \in W \setminus \set{i}:\\ e \in P_{ij}}} 1 \\
                        &= 1 \\
                        &= b(f_i).
                    \end{split}
                \]

                \item $f = r$.
                We have not been able, with the current definition of $y$ and $D^e$, to make this work.
                However, we reduced it to a more accessible form.
                In the third line, we exchange the order of the two sums and use the symmetry of $\pi_T(i, j)$ and $P_{ij}$.
                \[
                    \begin{split}
                        \sum_{\substack{ij \in \binom{W}{2},\\r \in \pi_T(i,j)}} d^e_{ij} &= \frac 1 2 \sum_{i \in W} \sum_{\substack{j \in W \setminus \set{i}:\\r \in \pi_T(i,j)}} d^e_{ij} \\
                        &= \frac{1}{2k} \sum_{i \in W} \sum_{\substack{j \in W \setminus \set{i}:\\r \in \pi_T(i,j),\\e \in P_{ij}}} \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} + \frac{1}{2k} \sum_{i \in W} \sum_{\substack{j \in W \setminus \set{i}:\\r \in \pi_T(i,j),\\e \in P_{ij}}} \frac{y(e, \mathcal P_j)}{n(e, \mathcal P_j)} \\
                        &= \frac{1}{2k} \sum_{i \in W} \sum_{\substack{j \in W \setminus \set{i}:\\r \in \pi_T(i,j),\\e \in P_{ij}}} \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} + \frac{1}{2k} \sum_{j \in W} \sum_{\substack{i \in W \setminus \set{j}:\\r \in \pi_T(j,i),\\e \in P_{ji}}} \frac{y(e, \mathcal P_j)}{n(e, \mathcal P_j)} \\
                        &= \frac{1}{k} \sum_{i \in W} \sum_{\substack{j \in W \setminus \set{i}:\\r \in \pi_T(i,j),\\e \in P_{ij}}} \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} \\
                        &= \frac{1}{k} \sum_{\substack{i \in W:\\n(e, \mathcal P_i) > 0}} \left( \alpha(e, \mathcal P_i) \frac{y(e, \mathcal P_i)}{n(e, \mathcal P_i)} \right) \\
                        &\ \vdots\\
                        &\le b(r).
                    \end{split}
                \] \qedhere
            \end{itemize}

        \end{proof}
        The remainder of the proof of Lemma~3 (and Claim~2) is exactly the same as in \cite{grandoni2008short}, as the definition of $D^e$ is exactly the same, and the definition of $y(e, \mathcal P_i)$ itself is not used.
    \end{proof}

    From this follows (our version of) Theorem~1, stating that on ring networks, if there exists an optimal tree solution for the \emph{genPR} problem, that also an optimal tree solution exists for the generalized VPN problem.

    Now, what remains to show is that indeed an optimal tree solution exists for the \emph{genPR} problem when $G$ is a ring.
    If we follow the structure of the proof in \cite{grandoni2008short}, not first that Claim~3 also holds for our case.
    However, Claim~4 does not hold: it might be that $y(e, \mathcal P_i) = y(f, \mathcal P_i) = b(r)$ (in the second case of the definition of $y$).
    We have not quite yet mastered the inductive proof that follows (in which Claim~4) is used.
    Therefore, we are not sure that the counterexample for Claim~4 is actually problematic, or how to circumvent this issue.

    \bibliographystyle{plain}
    \bibliography{references}

\end{document}
