\documentclass[11pt]{article}

\usepackage{float}
\usepackage[bookmarks=true]{hyperref}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage[fleqn]{amsmath}
\usepackage{graphicx}

\input{../macros.tex}

\theoremstyle{definition}
\newtheorem{fact}{Fact}
\newtheorem{conjecture}{Conjecture}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}

\title{Experiments and analysis for selected robust network design problem classes}
\author{David Dekker \\ \texttt{d.j.c.dekker@student.tue.nl} \and Sten Wessel \\ \texttt{s.wessel@student.tue.nl}}
\date{\today}

% Document
\begin{document}
    \maketitle
    \hrule
    \bigskip

    \section{Introduction} \label{sec:introduction}
    We consider a graph $G = (V, E)$ with a set of terminals $W \subseteq V$, together with a set of valid traffic demands between terminals represented by a matrix $(D_{ij})_{i,j \in W}$.
    We refer to the set of valid demands as the \emph{demand universe} $\mathcal U$.
    The goal in robust network design is to construct a network on $G$ by buying capacities on the edges such that every valid traffic demand can be routed on the network.
    The usual challenge is to minimize the cost of the network, defined by $\sum_{e \in E} c_e x_e$, where $x_e$ denotes the bought capacity for edge $e$, and $c_e$ the per-unit-capacity cost of the edge.

    Although the network needs to be able to route multiple demand matrices, we disallow changing the routing paths between terminals if demands change.
    This is referred to the \emph{oblivious} routing model, where each pair of terminals $i,j \in W$ has a fixed routing path $P_{ij}$ for all routing all demands.
    Hence, for every edge $e$ on the path $P_{ij}$ we must buy a capacity of at least $D_{ij}$, for each demand matrix $D \in \mathcal U$.
    We refer to the set of paths $\mathcal P = \set{P_{ij} : i,j \in W}$ as the \emph{routing template}.
    The routing template, together with the bought capacities for the edges, forms the solution to a robust network design problem.

    Robust network design has been studied on specific classes of demand universes.
    Such as special class are the \emph{hose matrices} $\mathcal H = \set{(D_{ij}) : \sum_j D_{ij} \le b_i \quad \forall_{i \in W}}$, where $b_i$ denotes the \emph{marginal} demand for terminal $i$, that describes the maximum amount of traffic communicated from this terminal.
    The demands are viewed as undirected, hence $D_{ij} = D_{ji}$ describes the single demand between $i,j$.
    Designing a minimum cost network for the class of hose matrices is known as the \emph{virtual private network (VPN) problem}.
    A $2$-approximation algorithm for the VPN problem was shown both in \cite{fingerhut1997designing} and \cite{gupta2001provisioning}.
    It was conjectured \cite{italiano2006design} that this algorithm is in fact optimal.
    The conjecture was initially shown to hold on ring networks (the constrained setting where $G$ is a cycle) and some other special cases~\cite{hurkens2007virtual}, and was later resolved for arbitrary networks as well~\cite{goyal2013vpn}.

    In this report, we consider two additional classes of (polyhedral) demand universes.
    We first look into \emph{tree demands}, generalizing the class of hose matrices.
    The robust network design problem for tree demands is known as the \emph{generalized VPN problem}.
    The 2-approximation algorithm for the VPN problem has a natural extension to the generalized case, and it is conjectured that this algorithm is optimal in this setting as well \cite{OLVER2016191}.
    However, this remains unresolved.
    In this report, we discuss this algorithm and discuss some efforts of proving the conjecture on ring networks.

    We then turn to a different class of demand matrices, called the \emph{capped hose model}.
    In this model, we consider the specific case where the terminals are given on a cycle demand graph and the terminals are only allowed to communicate traffic when they are direct neighbors on this cycle.
    For the unit-capacity case, it has been shown in \cite{bosman2017exploring} that minimizing the total network cost under this model is polynomial-time solvable.
    In this report, we discuss this algorithm and some efforts of extending this proof to the more general case.

    \input{genvpn}

    \input{cappedhose}

    \section{Conclusion}
    In this report, we have introduced the general robust network design problem type, and have discussed a number of specific classes of robust network design problems.
    A famous class of problems is formed by taking traffic demands from the hose model, where then the minimization of the total network cost is known as the VPN problem.
    For the VPN problem, it has been shown that it is polynomial-time solvable.
    We have furthermore discussed the classes of tree demands and the capped hose model, which characterize variations on the VPN problem for which it remains open whether the known constant-factor approximation algorithms are in fact optimal.
    We have discussed these algorithms, and described a number of experiments aimed at possibly finding a counterexample for optimality of these algorithms.
    We have also discussed some efforts of extending the proofs of optimality for restricted cases for the problem class in general.

    \bibliographystyle{plain}
    \bibliography{references}

    \clearpage
    \appendix
    \input{appendix}

\end{document}
